Quality measure notes

### 2021-07-24 StateOfPractice/Ao-Report/13Methods.tex
MI report - minor updates
MI report - updated software table in ch 4

\begin{itemize}
\item \textbf{Installability} We check the existence and quality of installation instructions. The user experience is also an important factor, such as the ease to follow the instructions, number of steps, automation tools, and the prerequisite steps for the installation. If any problem interrupts the process of installation or uninstallation, we give a lower score to this quality. We also record the operating system for the installation test and whether we can verify the installation.

\item \textbf{Correctness \& Verifiability} For \textit{correctness}, we check the projects to identify the techniques to ensure this quality, such as literate programming, automated testing, symbolic execution, model checking, unit tests, etc. We also examine whether the projects use continuous integration. For \textit{verifiability}, we go through the documents of the projects to check the requirements specifications, theory manuals, and getting started tutorials. If a getting started tutorial exists and provides expected results, we follow it and check if the outputs match.

@@

Then we followed the steps in Section \ref{sec_grading_software} to measure and grade the software. 27 out of the 29 packages are compatible with two or three different operating systems such as Windows, macOS, and Linux, and 5 of them are browser-based, making them platform-independent. However, in the interest of time, we only performed the measurements for each project by installing it on one of the platforms, most likely Windows.

>>>>

\begin{itemize}
\item \textbf{Installability} We check the existence and quality of installation instructions. The user experience is also an important factor, such as the ease to follow the instructions, number of steps, automation tools, and the prerequisite steps for the installation. If any problem interrupts the process of installation or uninstallation, we give a lower score to this quality. We also record the operating system (OS) for the installation test and whether we can verify the installation.

\item \textbf{Correctness \& Verifiability} For \textit{correctness}, we check the projects to identify the techniques to ensure this quality, such as literate programming, automated testing, symbolic execution, model checking, unit tests, etc. We also examine whether the projects use continuous integration and continuous delivery (CI/CD). For \textit{verifiability}, we go through the documents of the projects to check the requirements specifications, theory manuals, and getting started tutorials. If a getting started tutorial exists and provides expected results, we follow it and check if the outputs match.

@@

Then we followed the steps in Section \ref{sec_grading_software} to measure and grade the software. 27 out of the 29 packages are compatible with two or three different OS such as Windows, macOS, and Linux, and 5 of them are browser-based, making them platform-independent. However, in the interest of time, we only performed the measurements for each project by installing it on one of the platforms, most likely Windows.

### 2021-07-24 StateOfPractice/Ao-Report/14MeasurementResults.tex
MI report - updated software table in ch 4

Table \ref{tab_final_list} shows the 29 software packages that we measured. We tried to find the initial release dates in the documents, such as the introduction and release notes. We used the date of the latest change to each code repository to decide the latest update. We found out funding information for eight projects, and we are not sure about the rest.

We considered anyone who made at least one accepted commit to the source code as a contributor. Thus, it does not mean that any development team has are 100 long-term members. Many of these projects received change requests and code from the community, such as pull requests and git commits on GitHub.

Table \ref{tab_final_list} also shows the supported operating systems for each software package, and 25 of them could work on all three Windows (W), macOS (M), and Linux (L) systems. However, there was a significant difference in the philosophy to achieve cross-platform compatibility. Most of them were native software products, but five were naturally platform-independent web applications.

\begin{table}[H]
\begin{tabular}{lllllllll}
\hline
\multirow{2}{*}{Software} & \multirow{2}{*}{Released} & \multirow{2}{*}{Updated} & \multirow{2}{*}{Contributors} & \multirow{2}{*}{Funded} & \multicolumn{3}{c}{OS} & \multirow{2}{*}{Web} \\ \cline{6-8}
 &  &  &  &  & W & M & L &  \\ \hline
3D Slicer \cite{Kikinis2014} & 1998 & 2020-08 & 100 & X & X & X & X &  \\
Ginkgo CADx \cite{Wollny2020} & 2010 & 2019-05 & 3 &  & X & X & X &  \\
XMedCon \cite{Nolf2003} & 2000 & 2020-08 & 2 &  & X & X & X &  \\
Weasis \cite{Roduit2021} & 2010 & 2020-08 & 8 &  & X & X & X &  \\
MRIcroGL \cite{Rorden2021} & 2015 & 2020-08 & 2 &  & X & X & X &  \\
SMILI \cite{Chandra2018} & 2014 & 2020-06 & 9 &  & X & X & X &  \\
ImageJ \cite{Rueden2017} & 1997 & 2020-08 & 18 & X & X & X & X &  \\
Fiji \cite{Schindelin2012} & 2011 & 2020-08 & 55 & X & X & X & X &  \\
DicomBrowser \cite{Archie2012} & 2012 & 2020-08 & 3 &  & X & X & X &  \\
3DimViewer \cite{TESCAN2020} & unclear & 2020-03 & 3 & X & X & X &  &  \\
Horos \cite{horosproject2020} & unclear & 2020-04 & 21 &  &  & X &  &  \\
OsiriX Lite \cite{PixmeoSARL2019} & 2004 & 2019-11 & 9 &  &  & X &  &  \\
dwv \cite{Martelli2021} & 2012 & 2020-09 & 22 &  & X & X & X & X \\
Drishti \cite{Limaye2012} & 2012 & 2020-08 & 1 &  & X & X & X &  \\
\begin{tabular}[c]{@{}l@{}}BioImage Suite\\ Web \cite{Papademetris2005}\end{tabular} & 2018 & 2020-10 & 13 & X & X & X & X & X \\
OHIF Viewer \cite{Ziegler2020} & 2015 & 2020-10 & 76 &  & X & X & X & X \\
Slice:Drop \cite{Haehn2013} & 2012 & 2020-04 & 3 &  & X & X & X & X \\
GATE \cite{Jan2004} & 2011 & 2020-10 & 45 &  &  & X & X &  \\
ITK-SNAP \cite{Yushkevich2006} & 2006 & 2020-06 & 13 & X & X & X & X &  \\
ParaView \cite{Ahrens2005} & 2002 & 2020-10 & 100 & X & X & X & X & X \\
MatrixUser \cite{Liu2016} & 2013 & 2018-07 & 1 &  & X & X & X &  \\
DICOM Viewer \cite{Afsar2021} & 2018 & 2020-04 & 5 & X & X & X & X &  \\
INVESALIUS 3 \cite{Amorim2015} & 2009 & 2020-09 & 10 &  & X & X & X &  \\
\end{tabular}
\end{table}

\begin{table}[H]
\begin{tabular}{lllllllll}
\hline
\multirow{2}{*}{Software} & \multirow{2}{*}{Released} & \multirow{2}{*}{Updated} & \multirow{2}{*}{Contributors} & \multirow{2}{*}{Funded} & \multicolumn{3}{c}{OS} & \multirow{2}{*}{Web} \\ \cline{6-8}
 &  &  &  &  & W & M & L &  \\ \hline
medInria \cite{Fillard2012} & 2009 & 2020-11 & 21 &  & X & X & X &  \\
dicompyler \cite{Panchal2010} & 2009 & 2020-01 & 2 &  & X & X &  &  \\
MicroView \cite{ParallaxInnovations2020} & 2015 & 2020-08 & 2 &  & X & X & X &  \\
Papaya \cite{UTHSCSA2019} & 2012 & 2019-05 & 9 &  & X & X & X &  \\
AMIDE \cite{Loening2017} & 2006 & 2017-01 & 4 &  & X & X & X &  \\
Gwyddion \cite{Nevcas2012} & 2004 & 2020-11 & 38 &  & X & X & X &  \\ \hline
\end{tabular}
\caption{\label{tab_final_list}Final software list}
\end{table}

>>>>

Table \ref{tab_final_list} shows the 29 software packages that we measured. We tried to find the initial release dates (Rlsd) in the documents, such as the introduction and release notes. We did not find this date for two projects and marked them with ``?". We used the date of the latest change to each code repository to decide the latest update. We found out funding information (Fnd) for eight projects, and we are not sure about the rest.

We counted the number of contributors (NOC) and lines of code (LOC). we considered anyone who made at least one accepted commit to the source code as a contributor. Thus, it does not mean that any development team has are 100 long-term members. Many of these projects received change requests and code from the community, such as pull requests and git commits on GitHub.

Table \ref{tab_final_list} also shows the supported OS for each software package, and 25 of them could work on all three Windows (W), macOS (M), and Linux (L) systems. However, there was a significant difference in the philosophy to achieve cross-platform compatibility. Most of them were native software products, but five were naturally platform-independent web applications.

\begin{table}[H]
\begin{tabular}{llllllllll}
\hline
\multirow{2}{*}{Software} & \multirow{2}{*}{Rlsd} & \multirow{2}{*}{Updated} & \multirow{2}{*}{Fnd} & \multirow{2}{*}{NOC} & \multirow{2}{*}{LOC} & \multicolumn{3}{c}{OS} & \multirow{2}{*}{W} \\ \cline{7-9}
 &  &  &  &  &  & W & M & L &  \\ \hline
3D Slicer \cite{Kikinis2014} & 1998 & 2020-08 & X & 100 & 501451 & X & X & X &  \\
Ginkgo CADx \cite{Wollny2020} & 2010 & 2019-05 &  & 3 & 257144 & X & X & X &  \\
XMedCon \cite{Nolf2003} & 2000 & 2020-08 &  & 2 & 96767 & X & X & X &  \\
Weasis \cite{Roduit2021} & 2010 & 2020-08 &  & 8 & 123272 & X & X & X &  \\
MRIcroGL \cite{Rorden2021} & 2015 & 2020-08 &  & 2 & 8493 & X & X & X &  \\
SMILI \cite{Chandra2018} & 2014 & 2020-06 &  & 9 & 62626 & X & X & X &  \\
ImageJ \cite{Rueden2017} & 1997 & 2020-08 & X & 18 & 9681 & X & X & X &  \\
Fiji \cite{Schindelin2012} & 2011 & 2020-08 & X & 55 & 10833 & X & X & X &  \\
DicomBrowser \cite{Archie2012} & 2012 & 2020-08 &  & 3 & 5505 & X & X & X &  \\
3DimViewer \cite{TESCAN2020} & ? & 2020-03 & X & 3 & 178065 & X & X &  &  \\
Horos \cite{horosproject2020} & ? & 2020-04 &  & 21 & 561617 &  & X &  &  \\
OsiriX Lite \cite{PixmeoSARL2019} & 2004 & 2019-11 &  & 9 & 544304 &  & X &  &  \\
dwv \cite{Martelli2021} & 2012 & 2020-09 &  & 22 & 47815 & X & X & X & X \\
Drishti \cite{Limaye2012} & 2012 & 2020-08 &  & 1 & 268168 & X & X & X &  \\
\begin{tabular}[c]{@{}l@{}}BioImage Suite\\ Web \cite{Papademetris2005}\end{tabular} & 2018 & 2020-10 & X & 13 & 139699 & X & X & X & X \\
OHIF Viewer \cite{Ziegler2020} & 2015 & 2020-10 &  & 76 & 63951 & X & X & X & X \\
Slice:Drop \cite{Haehn2013} & 2012 & 2020-04 &  & 3 & 19020 & X & X & X & X \\
GATE \cite{Jan2004} & 2011 & 2020-10 &  & 45 & 207122 &  & X & X &  \\
ITK-SNAP \cite{Yushkevich2006} & 2006 & 2020-06 & X & 13 & 88530 & X & X & X &  \\
ParaView \cite{Ahrens2005} & 2002 & 2020-10 & X & 100 & 886326 & X & X & X & X \\
MatrixUser \cite{Liu2016} & 2013 & 2018-07 &  & 1 & 23121 & X & X & X &  \\
\end{tabular}
\end{table}

\begin{table}[H]
\begin{tabular}{llllllllll}
\hline
\multirow{2}{*}{Software} & \multirow{2}{*}{Rlsd} & \multirow{2}{*}{Updated} & \multirow{2}{*}{Fnd} & \multirow{2}{*}{NOC} & \multirow{2}{*}{LOC} & \multicolumn{3}{c}{OS} & \multirow{2}{*}{W} \\ \cline{7-9}
 &  &  &  &  &  & W & M & L &  \\ \hline
DICOM Viewer \cite{Afsar2021} & 2018 & 2020-04 & X & 5 & 30761 & X & X & X &  \\
INVESALIUS 3 \cite{Amorim2015} & 2009 & 2020-09 &  & 10 & 48605 & X & X & X &  \\
medInria \cite{Fillard2012} & 2009 & 2020-11 &  & 21 & 148924 & X & X & X &  \\
dicompyler \cite{Panchal2010} & 2009 & 2020-01 &  & 2 & 15941 & X & X &  &  \\
MicroView \cite{ParallaxInnovations2020} & 2015 & 2020-08 &  & 2 & 27470 & X & X & X &  \\
Papaya \cite{UTHSCSA2019} & 2012 & 2019-05 &  & 9 & 71831 & X & X & X &  \\
AMIDE \cite{Loening2017} & 2006 & 2017-01 &  & 4 & 102827 & X & X & X &  \\
Gwyddion \cite{Nevcas2012} & 2004 & 2020-11 &  & 38 & 643427 & X & X & X &  \\ \hline
\end{tabular}
\caption{\label{tab_final_list}Final software list}
\end{table}

### 2021-07-24 StateOfPractice/Ao-Report/15InterviewsWithDevelopers.tex
MI report - updated software table in ch 4

\begin{table}[H]
\centering
\begin{tabular}{llll}
\hline
\multirow{2}{*}{Group} & \multirow{2}{*}{Obstacle} & \multicolumn{2}{l}{Number of interviewees with the answer} \\ \cline{3-4} 
 &  & as a current obstacle & as a past obstacle \\ \hline
\multirow{2}{*}{1} & Lack of fundings & 3 &  \\
 & Lack of time to devote to the project & 2 & 1 \\ \hdashline
\multirow{3}{*}{2} & \begin{tabular}[c]{@{}l@{}}Hard to keep up with changes in operating \\ systems and libraries\end{tabular} & 1 &  \\
 & Hard to support multiple operating systems & 2 &  \\
 & Hard to support lower-end computers & 1 & 2 \\ \hdashline
3 & Lack of access to real-world datasets for testing & 3 & 2 \\ \hdashline
\multirow{7}{*}{Others}
 & Hard to have a high level roadmap from the start & 1 &  \\
 & Not enough participants for usability tests & 1 &  \\
 & \begin{tabular}[c]{@{}l@{}}Codebase is so big and complicated and only\\ a few people fully understand it\end{tabular} & 1 &  \\
 & Hard to transfer to new technologies & & 2 \\
 & Hard to understand users' needs & & 1 \\
 & Hard to maintain good documentations & & 1 \\ \hline
\end{tabular}
\caption{\label{tab_obstacles}Current and past obstacles by the numbers of interviewees with the answers}
\end{table}

>>>>

\begin{table}[H]
\centering
\begin{tabular}{llll}
\hline
\multirow{2}{*}{Group} & \multirow{2}{*}{Obstacle} & \multicolumn{2}{l}{Number of interviewees with the answer} \\ \cline{3-4} 
 &  & as a current obstacle & as a past obstacle \\ \hline
\multirow{2}{*}{1} & Lack of fundings & 3 &  \\
 & Lack of time to devote to the project & 2 & 1 \\ \hdashline
\multirow{3}{*}{2} & \begin{tabular}[c]{@{}l@{}}Hard to keep up with changes in OS \\ and libraries\end{tabular} & 1 &  \\
 & Hard to support multiple OS & 2 &  \\
 & Hard to support lower-end computers & 1 & 2 \\ \hdashline
3 & Lack of access to real-world datasets for testing & 3 & 2 \\ \hdashline
\multirow{7}{*}{Others}
 & Hard to have a high level roadmap from the start & 1 &  \\
 & Not enough participants for usability tests & 1 &  \\
 & \begin{tabular}[c]{@{}l@{}}Codebase is so big and complicated and only\\ a few people fully understand it\end{tabular} & 1 &  \\
 & Hard to transfer to new technologies & & 2 \\
 & Hard to understand users' needs & & 1 \\
 & Hard to maintain good documentations & & 1 \\ \hline
\end{tabular}
\caption{\label{tab_obstacles}Current and past obstacles by the numbers of interviewees with the answers}
\end{table}
